% Intended LaTeX compiler: pdflatex
\documentclass{custom}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{John Doe}
\date{\today}
\title{John Doe}
\hypersetup{
 pdfauthor={John Doe},
 pdftitle={John Doe},
 pdfkeywords={Python, Go, Software Engineering, API Development, Distributed Systems},
 pdfsubject={Senior Software Engineer},
 pdfcreator={Emacs 30.2 (Org mode 9.7.34)},
 pdflang={English}}
\cvtagline{Software Engineering - Distributed Systems - Developer Tooling}
\cvsummary{Experienced Software Engineer delivering scalable backend systems across distributed environments and cross-functional teams.}
\begin{document}

\maketitle
\heading
\contactinfo{Amsterdam, Netherlands}{31612345678}{+31 6 12 345 678}{john.doe@example.com}{johndoe}{https://johndoe.dev}
\section{Senior Software Engineer}
\label{introduction}
\introduction

\textbf{Software engineer} with over ten years of experience building scalable backend
services, distributed systems, and developer tooling. Focused on writing clean,
maintainable code and collaborating effectively across teams to deliver reliable
software at pace.
\section{Career Highlights}
\label{career-highlights}
\textbf{Highlight one}: Led the migration of a monolithic payment processing service to a microservices
architecture, enabling independent deployments and reducing team release cycles
from two weeks to daily with no regression in stability.
\\[0.2\baselineskip]
\textbf{Highlight two}: Designed and built a real-time event ingestion pipeline capable of sustaining peak
traffic without data loss, replacing a fragile batch-based approach that had caused
repeated customer-facing outages.
\\[0.2\baselineskip]
\textbf{Highlight three}: Introduced structured observability practices — distributed tracing, standardised
logging, and service-level dashboards — across a platform team, significantly reducing
mean time to resolution during production incidents.
\\[0.2\baselineskip]
\section{Strengths Snapshots}
\label{strengths-snapshots}
\begingroup\renewcommand{\arraystretch}{1.4}\setlength{\tabcolsep}{8pt}
\begin{center}
\begin{tabularx}{\textwidth}{@{}XXX@{}}
\textbullet{} API Design \& Development & \textbullet{} Distributed Systems & \textbullet{} Cloud Infrastructure (AWS)\\
\textbullet{} Test-Driven Development & \textbullet{} System Design & \textbullet{} Code Review \& Mentorship\\
\textbullet{} CI/CD Pipeline Automation & \textbullet{} Database Design & \textbullet{} Observability \& Monitoring\\
\end{tabularx}
\end{center}
\endgroup\vspace{-0.1cm}
\section{Software Engineering Experience and Milestones}
\label{experience}
\position{Senior Software Engineer}{Stripe}{Netherlands, Amsterdam, Remote}{March 2022 - Current}

\begin{cvdescription}
Part of the developer platform team responsible for internal tooling and APIs used by
600+ engineers across the organisation. Brought in to improve the reliability and
consistency of service infrastructure patterns as the platform scaled.
\end{cvdescription}

\begin{itemize}\setlength{\itemsep}{-2pt}
\item Led the redesign of the internal service mesh configuration system, standardising patterns across services and reducing deployment times.
\item Built a distributed rate-limiting service handling millions of requests per second, improving reliability for payment integrations.
\end{itemize}
\position{Senior Software Engineer}{Datadog}{Netherlands, Amsterdam, Remote}{January 2020 - February 2022}

\begin{cvdescription}
Worked on the metrics ingestion pipeline responsible for processing billions of data
points daily. Joined to help the team tackle performance bottlenecks and extend the
platform to support new customer data types at scale.
\end{cvdescription}

\begin{itemize}\setlength{\itemsep}{-2pt}
\item Redesigned the metadata enrichment layer, improving query accuracy and reducing per-event processing overhead.
\item Rewrote a legacy Go service handling metric aggregation, enabling the team to extend functionality previously blocked by technical debt.
\item Set up contract testing in CI, catching breaking API changes before they reached production.
\item Mentored junior engineers, establishing Go idioms and code review standards adopted across the backend guild.
\end{itemize}
\position{Senior Software Engineer}{Thoughtworks}{Germany, Berlin, Remote}{June 2018 - December 2019}

\begin{cvdescription}
Delivered backend solutions across multiple client engagements in fintech and
e-commerce. Responsible for technical leadership on client projects from discovery
through to production, working closely with product and design stakeholders.
\end{cvdescription}

\begin{itemize}\setlength{\itemsep}{-2pt}
\item Designed the core data model and REST API for a payments platform, forming the foundation for the client's first production release.
\item Introduced trunk-based development and feature flag practices, improving release cadence and reducing merge friction across teams.
\item Built an event delivery system with retry logic and dead-letter queuing, improving reliability for third-party integrations.
\end{itemize}
\position{Software Engineer}{Booking.com}{Netherlands, Amsterdam, Hybrid}{January 2016 - May 2018}

\begin{cvdescription}
Part of the supply integration team responsible for connecting hotel property
management systems to the Booking platform. Worked within a large distributed
engineering organisation to maintain and extend high-volume data pipelines.
\end{cvdescription}

\begin{itemize}\setlength{\itemsep}{-2pt}
\item Built a sync service processing millions of availability and pricing updates daily from 50+ external partners.
\item Developed an internal reporting dashboard that replaced manual data exports, saving significant weekly effort for the operations team.
\item Created reusable Terraform modules for service infrastructure, adopted across eight product teams.
\end{itemize}
\position{Software Engineer}{Backbase}{Netherlands, Amsterdam, Remote}{September 2013 - December 2015}

\begin{cvdescription}
Worked on the core banking platform, contributing to features used by over 30 banking
clients worldwide. Joined as a mid-level engineer and grew into ownership of key
modules within the notification and scheduling subsystems.
\end{cvdescription}

\begin{itemize}\setlength{\itemsep}{-2pt}
\item Migrated email and notification templates from a legacy Velocity engine to a modern React-based renderer, improving customisation speed and flexibility.
\item Fixed a critical bug in the scheduling module that had caused intermittent failures in overnight batch jobs for multiple clients.
\item Wrote API documentation that significantly reduced support tickets raised by client integration teams.
\end{itemize}
\priorheading
\priorposition{Junior Software Developer}{Coolblue}{Netherlands, Rotterdam}{June 2012 - August 2013}
\priorposition{Software Development Intern}{TU Delft — Research Group}{Netherlands, Delft}{February 2011 - May 2012}
\section{Education}
\label{education}
\begin{center}
\begin{tabular*}{\textwidth}{@{}l@{\hspace{0.5em}}l@{}}
\textbf{Master of Science (Computer Science)} & – University of Amsterdam, Amsterdam, Netherlands\\
\textbf{Bachelor of Science (Computer Science)} & – Delft University of Technology, Delft, Netherlands\\
\end{tabular*}
\end{center}
\section{Technical Acumen}
\label{technical-acumen}
Technical acumen includes, but is not limited to:

\begin{center}
\begin{tabularx}{\textwidth}{l@{\hspace{1em}}X}
\textbf{Programming Languages}: & \emph{Python}, \emph{Go} and \emph{TypeScript}.\\
\textbf{Databases}: & \emph{PostgreSQL} and \emph{Redis}.\\
\textbf{Messaging \& Streaming}: & \emph{Apache Kafka} and \emph{RabbitMQ}.\\
\textbf{Infrastructure \& Cloud}: & \emph{Docker}, \emph{Kubernetes} and \emph{AWS}.\\
\textbf{Libraries \& Frameworks}: & \emph{FastAPI}, \emph{gRPC} and \emph{React}.\\
\textbf{Data \& Analytics}: & \emph{Apache Spark} and \emph{dbt}.\\
\end{tabularx}
\end{center}
\section{Language Proficiencies}
\label{languages}
English (Fluent) and Dutch (Conversational).
\end{document}
